Sampling requirements to detect ecosystem change

### 2020-01-15 R/manuscript_draft.Rmd
eval=T for case studies figures

```{r case study read data output, include=FALSE,eval=F}
myoutput <- read.table(paste0(getwd(),"/Output/output_changepoint_varese.txt"))
myoutput$method_f <- factor(myoutput$method, levels=c('Random', 'Regular', 'Iterative'))

@@

```{r echo=FALSE, message=FALSE, warning=FALSE,eval=F}
library(ggplot2)
library(gridExtra)
p1 <- ggplot(myoutput, aes(final_n,diff_real)) + 
  geom_point(alpha = .3) +
  facet_wrap(~method_f) + theme_bw() +
  labs(title="a",x="", y="Distance to real changepoint")
p2 <- ggplot(myoutput, aes(rep(0, nrow(myoutput)),diff_real))  +
  facet_wrap(~method_f) + 
  geom_violin() +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=.3) + 
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + theme_bw() +
  labs(title="b",x="", y="Distance to real changepoint")
grid.arrange(p1, p2, nrow = 2)
```

>>>>

```{r case study read data output, include=FALSE}
myoutput <- read.table(paste0(getwd(),"/Output/output_changepoint_varese.txt"))
myoutput$method_f <- factor(myoutput$method, levels=c('Random', 'Regular', 'Iterative'))

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(gridExtra)
p1 <- ggplot(myoutput, aes(final_n,diff_real)) + 
  geom_point(alpha = .3) +
  facet_wrap(~method_f) + theme_bw() +
  labs(title="a",x="", y="Distance to real changepoint")
p2 <- ggplot(myoutput, aes(rep(0, nrow(myoutput)),diff_real))  +
  facet_wrap(~method_f) + 
  geom_violin() +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=.3) + 
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + theme_bw() +
  labs(title="b",x="", y="Distance to real changepoint")
grid.arrange(p1, p2, nrow = 2)
```
